---
title: "FDS Final Project: Report #3"
output: html_document
---

### using get content I have to show the results.

# Part 1

#### What are the highest grossing dramas from 2010?

For the first part, I used the following link : 
https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&with_genres=18&primary_release_year=2010&sort_by=revenue.desc

```{r Setup, include= FALSE}

library(rvest)
library(tidyverse)
library(data.table)
library(httr)
library(purrr)
```

```{r Part 1, include= FALSE}

knitr::opts_chunk$set(echo=FALSE, message  = FALSE, warning = FALSE)

find2 <- "https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&with_genres=18&primary_release_year=2010&sort_by=revenue.desc"

find2 %>% 
  GET() %>% 
  content() %>% 
  pluck("results") %>% 
  map_chr(pluck, "title")

```

#### Have Will Ferrell and Liam Neeson even been in a movie together?

```{r Part 1-2, include= TRUE}

find3 <- "https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&with_people=23659,3896&sort_by=vote_average.desc"

find3 %>% 
  GET() %>% 
  content() %>% 
  pluck("results") %>% 
  map_chr(pluck, "title")

```

Then, with the following link :
https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&with_people=23659,3896&sort_by=vote_average.desc

I found the total results of 4.

#### Can you find kids movies with Tom Cruise in it?

```{r Part 1-3, include= TRUE}

find4 <- "https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&certification.lte=G&with_people=500&sort_by=popularity.desc"

find4 %>% 
  GET() %>% 
  content() %>% 
  pluck("results") %>% 
  map_chr(pluck, "title")

```

Finally, using the following link :
https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&certification.lte=G&with_people=500&sort_by=popularity.desc

I got the following result : 85.

# Part 2

```{r part 2}

Pixar <- GET("http://api.themoviedb.org/3/search/company?api_key=1832bdfef330f3b47949f5545e56c0a1&query=Pixar&page=1")

Pixar_id <- httr::content(Pixar, as = "parsed")

Pixar_iddd <- Pixar_id$results[[1]]$id

# New code example below (53)

Pixar_id %>% pluck("results", 1, "id")

```
For the part 2, U used the following link : 
https://api.themoviedb.org/3/search/company?api_key=1832bdfef330f3b47949f5545e56c0a1&query=Pixar&page=1

As I saw in the code for this exercice, I was able to see the id result.

# Part 3

```{r part 3}

find2 <- paste("https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&language=en-US&sort_by=popularity.desc&include_adult=false&include_video=false&page=%d&with_companies=",Pixar_iddd,"&with_watch_monetization_types=flatrate")

find2 %>% 
  GET() %>% 
  content() %>% 
  pluck("results") %>% 
  map_chr(pluck, "title")

# Unit and modify the line 75 to 81 to et the result

data_pop <- find2 %>% 
  GET() %>% 
  content() %>% 
  pluck("results") %>% 
  map_df(magrittr::extract, c("title", "popularity"))

map_dfr(1:7, function(i) {
  resul2<- httr::GET(sprintf(find2, i))
  result2_pixar<- content(resul2, "parsed")
  data.frame(t(sapply(result2_pixar$results ,c)))
  })

# resul2<- httr::GET(find2)

# result2_pixar<- content(resul2, "parsed")

data_pixar <- data.frame(t(sapply(result2_pixar$results ,c)))

```

For the part 3, I used the following link :
https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&language=en-US&sort_by=popularity.desc&include_adult=false&include_video=false&page=1&with_companies=

```{r part }

print(head(data_pixar[,1:4]))

```

We are printing the first 6 observations to have an overview of the data set.

```{r part 4}

Disney <- GET("http://api.themoviedb.org/3/search/company?api_key=1832bdfef330f3b47949f5545e56c0a1&query=Disney&page=1")

Disney_list <- httr::content(Disney, as = "parsed")

Disney_listtt <- Disney_list$results[[7]]$id

find22 <- "https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&sort_by=popularity.desc&include_video=false&page=%d&with_companies=3"

map_dfr(1:7, function(i) {
  
  resul2<- httr::GET(sprintf(find22, i))
  
  result2_pixar<- content(resul2, "parsed")
  
  data.frame(t(sapply(result2_pixar$results ,c)))

}) -> data_pixar

find3 <- "https://api.themoviedb.org/3/discover/movie?api_key=1832bdfef330f3b47949f5545e56c0a1&sort_by=popularity.desc&include_video=false&page=%d&with_companies=2"

map_dfr(1:32, function(i) {
  
  resul3<- httr::GET(sprintf(find3, i))
  
  result3_disney<- content(resul3, "parsed")
  
  data.frame(t(sapply(result3_disney$results ,c)))

}) -> data_disney

data_disney <- data_disney[,-(15:34)]  

data_pixar$release_date=unlist(data_pixar$release_date)

data_pixar$release_date<- as.Date(data_pixar$release_date, "%Y-%m-%d")

data_pixar <- data_pixar %>% 
  filter(release_date >= "2006-01-01") %>% 
  filter(vote_count>50)

data_disney <-data_disney[!data_disney$release_date == "NULL", ] 
data_disney <-data_disney[!data_disney$release_date == "", ] 

data_disney$release_date=unlist(data_disney$release_date)

data_disney$release_date<- as.Date(data_disney$release_date, "%Y-%m-%d")

data_disney <- data_disney%>% 
  filter(release_date >= "2006-01-01") %>% 
  filter(vote_count>50)

x<-cbind(rep("pixar",length(data_pixar$release_date))
,data_pixar$vote_average)

y<-cbind(rep("disney",length(data_disney$release_date))
,data_disney$vote_average)

films_comparision<- data.frame(rbind(x,y))

colnames(films_comparision)=c("Companies","Vote_average")

films_comparision$Vote_average=as.numeric(films_comparision$Vote_average)

films_comparision$Companies=as.character(films_comparision$Companies)

ggplot(data = films_comparision, aes(x= Companies, y = Vote_average)) +
  geom_boxplot()+
  labs(title="Vote comparison by companies")

t.test(Vote_average ~ Companies, data=films_comparision )

```

Looking at the part 4, few steps was needed. Indeed, I had to save mutliples variables from Disney for example and using function such as "sapply".

I also had to remove some null values columns.

I applied statistical analysis. 

For that I had to filter the year 2006, and transform release data as a date format (it was character initialy).

I actually applied the same process for Disney and eliminated nulll value as well.

I could then run the boxplot and t.test. It was important to verify that it were numerical values.

On the bloxplot, we can see a difference, but to know if it is a significant difference so we have to apply a t test (independent sample t test)

#### Answering to the following question : 

Are the films from Pixar on average more popular than the films from Walt Disney Pictures?

Based on the output, which p-value = 0.01849, so first there is a significant difference between vote average from disney and pixar, which means that on average, pixar has a highest score than disney.
